### 2011-01-26 paper/platformDetails.tex
Added info about min and max servo positions

The robot is run using a given motion model, including, if desired, 
smooth interpolation over time for the beginning and end of the run. 
The servos are prevented from being commanded to a point outside their
normal range (0 - 1023) as well as beyond points where limbs would collide.

>>>>

The robot is run using a given motion model, including, if desired, 
smooth interpolation over time for the beginning and end of the run. 
The servos are prevented from being commanded to a point outside their
normal range (0 - 1023) as well as beyond points where limbs would collide
(150 - 770 for inner leg servos, 30 - 680 for outer leg servos, and 392 - 623
for the center, or "hip" servo.
